---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Fnpol Package

<!-- badges: start -->
[![documentation](https://img.shields.io/badge/documentation-fnpol-green.svg)](https://github.com/vincehass/Advanced-Computational-Statistics-and-Functional-Programming/tree/master/1-Fnpol)
[![contributions](https://img.shields.io/badge/contributions-welcome-red.svg)](https://github.com/vincehass/Advanced-Computational-Statistics-and-Functional-Programming/tree/master/1-Fnpol)
[![check](https://img.shields.io/badge/check-passed-green.svg)](https://github.com/vincehass/Advanced-Computational-Statistics-and-Functional-Programming/tree/master/1-Fnpol)
<!-- badges: end -->

The goal of fnpol is to provide functionalities for fast computation for the following methods: 
              Fast fourrier methods, random variable generator and polynomials series.

### Author: Nadhir Hassen


## Installation
You need to load `usethis::use_package(devtools)` and `library(devtools)`.
You can install the released version of **fnpol** from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fnpol")
```

```{r setup}
library(fnpol)
library(devtools)
devtools::load_all()
```

This package describes functionalities for fast computation with the following methods: 
Fast fourier method `fft_c2`, random variable simulator which provides transformation such as sum `simulateur_sum`, proportion `simulateur_prop` and summary distribution `simulateur_bar`. In addition, we provide a class of polynomial that return a symbolic polynomials, their transformation such that sum of polynomials, multiplication of polynomials, derivative of polynomials and summary statistics which give their respective factorization.


## Fast Fourier Method
The fourier transform is defined as the sum of $N$ complexs number  $(X_k)_{k=0}^{N-1}$ such that

\begin{equation}
    \begin{split}
X_k = \sum_{n=0}^{N-1}x_n \exp\left(-2\pi i k \frac{n}{N}\right)
    \end{split}
\end{equation}
where $i$ is the imaginary part and the complex serie $(x_n)_{n=0}^{N-1}$  $\in \mathbb{C}$.

### Naive form Fast Fourier Transform
```{r}
vec_com<-sample(complex(real=sample(1:20,16), imaginary = sample(1:20,16)),16)
vec_com
dft1_naive(vec_com,k=3)
```

### Iterative Form for Fast Fourier Transform
```{r}

dft1_iter(vec_com,k=3)
```
### Matrix Form for Fast Fourier Transform
```{r}

dft1_matrix(vec_com,k=3)
```
### Comparaison of all methods for Fast Fourier Transform
```{r}
c(all.equal(dft_factory_all(vec_com)[,1], Im(fft(vec_com))),
  all.equal(dft_factory_all(vec_com)[,2], Im(fft(vec_com))),
  all.equal(dft_factory_all(vec_com)[,3], Im(fft(vec_com))))
```




### Fibonacci sequence
```{r}
fib_mulPos_rec(3)
```
###  Scalable Fast Fourier Transform

We use a recursive algorithm to calculate the fast Fourier transform. This method allows us to benefit from an important concept in algorithmic "divide to conquer". For this we decompose the Fourier transform into an even and odd sequence and exploit the symmetry of this decomposition such that


\begin{equation}
    \begin{split}
X_k &= \sum_{n=0}^{N-1} x_n \cdot e^{-i~2\pi~k~n~/~N} \\
    &= \sum_{m=0}^{N/2-1} x_{2m} \cdot e^{-i~2\pi~k~(2m)~/~N} + \sum_{m=0}^{N/2-1} x_{2m+1} \cdot e^{-i~2\pi~k~(2m+1)~/~N} \\
    &= \sum_{m=0}^{N/2-1} x_{2m} \cdot e^{-i~2\pi~k~m~/~(N/2)} + e^{-i~2\pi~k~/~N} \sum_{m=0}^{N/2-1} x_{2m+1} \cdot e^{-i~2\pi~k~m~/~(N/2)}
    \end{split}
\end{equation}

Using symmetry allows us to halve the computational complexity by going from $\mathcal{O}(N^2)$ to $\mathcal{O}(M^2)$, for $0\leq k < N$ and $0\leq n <M / 2$. In addition, using the recursive method has allowed us to further reduce this complexity. Therically this method reaches a complexity (assymptotically) of $\mathcal{O}(N\log N)$. We implement the algorithm below.

```{r}
fft_ct2(vec_com)
```

## Comparaison tool Fast Fourier Transform

```{r}
all.equal(fft_ct2(vec_com), fft(vec_com))
```


## Generator of random variable

### Generator of a transformed Discrete distribution

This function generate a vector of realization from the same distribution of the input vector. The user can specify a transformation on the input vector otherwise it will return the identity transformation.

```{r}
f2<-function(x) x**2;
xs<-c(10,3,5,20,4,6);
simulator_tran<-function(xs,trans=identity) lapply(list(length(xs)),simulator(xs, trans))
sim_tran<-simulator_tran(xs)
```


### Generator of a sum of random variables
This function allows to the user to generate the sum of two generators. The user could specify a transformation for the input otherwise it will return the identity transformation. We give two examples, the first with no transformation and the second with a transformation such as $f(x) = x^2$.

```{r}
simulator_sum<-function(v1,v2,trans=identity){
lapply(list(length(c(v1,v2))),realization_sum(v1,v2, trans))};
simulator_sum(c(1,2,3),c(2,3,4), identity);
f2<-function(x) x**2;
sim_sum<-simulator_sum(c(1,2,3),c(2,3,4), f2);
sim_sum
```

### Proportion of the simulated random variable
```{r}
f2<-function(x) x**2;
xs<-c(10,3,5,20,4,6);
sim_tran<-simulator_tran(xs)
sim_tran2<-simulator_tran(xs,f2);
simulator_prop(sim_tran);
simulator_prop(sim_tran2)
```

### Histogram of realized random variables

```{r}
f2<-function(x) x**2;
xs<-c(10,3,5,20,4,6);
sim_tran<-simulator_tran(xs)
sim_tran2<-simulator_tran(xs,f2);
simulator_prop(sim_tran);
simulator_bar(sim_tran);
simulator_bar(sim_tran2)
```

### Random variable Sequence Generator 
This function allows to calculate the longest bounded sequence given a defined arithmetic operation. We can simply track the decomposition of a selected operation. The `tracking_operator` takes as input the `sequence_long` which is the the sequence generator, `k` the index of a given result and `i` the operation performed to get the result. We have restrict ourselves to $5$ operations per set of number sampled, where $1\leq i\leq 5$ and $1\leq k\leq 5000$. 

```{r}
w<-sequence_long(sets = c(2L, 2L, 5L, 6L, 6L, 6L, 7L, 9L),
lowerb = -1e10,
upperb = 1e10)
tracking_operator(data = w, k=30,i=4)
tracking_operator(data = w, k=10, i=5)
```

## Algebric description of Polynomials

The `PlynR` class allows to construct a family of polynomials in order to manipulate arithmetic operations on polynomials and provide their algebric decompisition. eg.: sum, multiplication, roots and factorization.

### Algebric expression of a simple Polynom
```{r}
printPol.plynR(c(1,2,30))
```

### Algebric expression of a sum of Polynoms

```{r}
printPol.plynR(plus.plynR(c(1,1,10), c(1,2,10)))
```

### Algebric expression of a multiplication of Polynoms

```{r}
printPol.plynR(fois.plynR(c(1,1,10), c(1,2,10)))
```

### Algebric expression of a derivative of a Polynom

```{r}
printPol.plynR(derive.plynR(c(1,1,10)))
```


### Summary of Polynom with its factorization

```{r}
summaryPol.plynR(plynR(c(1,2,3)))
```


You can check more the description on Cran!
