---
title: "Fnpol vignette"
author: "Nadhir Hassen"
date: "`r Sys.Date() `"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fnpol_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fnpol)
```

This package describes functionalities for fast computation with the following methods: 
enhanced Fast fourrier method `fft_c2`, random variable simulator for differents sets of operators such as sum `simulateur_sum`, proportion `simulateur_prop` and summary distribution `simulateur_prop` , inverse and `simulateur_bar`. In addition, we provide a class of polynomial that return a differents polynomials transformation such that sum of polynomials, multiplication of polynomials, derivative of polynomials and summary statistics.


## Naive form Fast Fourier Inverse
```{r}

dft1_naive(vec_com,ki=3)
```

## Iterative Form for Fast Fourier Transform
```{r}

dft1_iter(vec_com,ki=3)
```
## Matrix Form for Fast Fourier Transform
```{r}

dft1_matrix(vec_com,ki=3)
```
## Comparaison of all methods for Fast Fourier Transform
```{r}
c(all.equal(dft_factory_all(vec_com)[,1], Im(fft(vec_com))),
  all.equal(dft_factory_all(vec_com)[,2], Im(fft(vec_com))),
  all.equal(dft_factory_all(vec_com)[,3], Im(fft(vec_com))))
```




## Fibonacci sequence
```{r}
fib_mulPos_rec(3)
```
## Scalable Fast Fourier Transform
```{r}
fft_ct2(com_vec)
```

## Comparaison tool Fast Fourier Transform
```{r}
all.equal(fft_ct2(com_vec), fft(com_vec))
```


